Storing messages with multipartite neural cliques

### 2014-07-18 Articles/article.tex
adaptation figure a = 2

\begin{figure}[!h]
\centering
\begin{tikzpicture}
  \foreach \type/\fill/\xshift/\yshift in {circle/draw/-50pt/50pt,rectangle/draw/50pt/50pt,rectangle/fill/-50pt/-50pt,circle/fill/50pt/-50pt}{
    \begin{scope}[xshift=\xshift,yshift=\yshift]
    \tikzstyle{every node}=[\type,draw,\fill];
    \foreach \i in {0,20pt,40pt,60pt}{
      \foreach \j in {0,20pt,40pt,60pt}{
        \node (node\type\fill\i\j) at (\i,\j) {};
      }
    }
\end{scope}
  }
  %% \path
  %% (nodecircledraw20pt40pt) edge (nodecirclefill040pt)
  %% edge (noderectanglefill20pt20pt)
  %% edge (noderectangledraw60pt60pt)
  %% (nodecirclefill040pt) edge (noderectanglefill20pt20pt)
  %% edge (noderectangledraw60pt60pt)
  %% (noderectanglefill20pt20pt) edge (noderectangledraw60pt60pt)
  %% ;
  %% \path
  %% (nodecircledraw60pt60pt) edge (nodecirclefill40pt20pt)
  %% edge (noderectanglefill060pt)
  %% edge (noderectangledraw20pt40pt)
  %% (nodecirclefill40pt20pt) edge (noderectanglefill060pt)
  %% edge (noderectangledraw20pt40pt)
  %% (noderectanglefill060pt) edge (noderectangledraw20pt40pt)
  %% ;
  \path[ultra thick]
  (nodecircledraw020pt) edge (nodecirclefill20pt20pt)
  edge (noderectanglefill40pt60pt)
  edge (noderectangledraw60pt60pt)
  (nodecirclefill20pt20pt) edge (noderectanglefill40pt60pt)
  edge (noderectangledraw60pt60pt)
  (noderectanglefill40pt60pt) edge (noderectangledraw60pt60pt)
  ;
\end{tikzpicture}
\caption{Illustration of the storage process of a message $\mu$. In this setting the number of clusters is $c=4$, each containing $\ell=16$ units. The parameter $a$ is 2.}
\label{fig:storage}
\end{figure}

@@

		\begin{align*}
		&\tilde{\mu}'[(j-1)l+k] =\\ \bigg \{
  			&\begin{tabular}{cl}
  			$1$ & if $s[(j-1)l+k] \ge  \mbox{select}(\alpha, s[(j-1)\ell+1 \hdots j\ell])$ \\
  			$0$ & otherwise 
  		         \end{tabular}\;.
  		\end{align*}
                Thus we use an Heavyside function with a parameter depending on each cluster. $\tilde{\mu}'$ is the output of the algorithm after one iteration. The process can be repeated providing $\tilde{\mu}'$ as the new input to the network. Several stopping criterion can be used~\cite{Ala}. In the remaining of this work, we will consider the number of iterations to be fixed. Simulations show that increasing the number of iterations can result in significatively better performance.

@@

	\begin{align}
		\label{formula_density}
		d = 1 - \left( 1 - \left(\frac{a}{l}\right)^2 \right)^m 
	\end{align}		
	, recalling that $m$ is the number of messages in $\mathcal{M}$.

@@

	The network is a binary symmetric matrix with null diagonal and can therefore be stored in memory as $\frac{c(c-1) l^2}{2}$ bits. Since messages are not stored in an ordered fashion, the entropy of the set of messages is $\log_2(\frac{({l \choose a}^c)^m}{m!}) \mathop{=}_{m \rightarrow +\infty} m(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} + o(1)) $ (thanks to  Stirling's formula). The ratio of information effectively stored in the network is $P_{retrieve} \times  \frac{2m \left(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} \right)}{c(c-1)l^2}$.

	Ambiguities would occur in a perfect associative memory if at least two messages were identical over non-erased letters. The probability it doesn't happen is $ (1-{l \choose a}^{c - c_e})^{m-1}$.

	$\eta_m = P_{retrieve}  \frac{2 m\left(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} \right)}{c(c-1)l^2} \times (1-(\frac{1}{{l \choose a}})^{c - c_e})^{-(m-1)}$
	%\frac{c}{(c-c_e) \log_2{l \choose a }}

>>>>

\begin{figure}[!h]
\centering
\begin{tikzpicture}
  \foreach \type/\fill/\xshift/\yshift in {circle/draw/-50pt/50pt,rectangle/draw/50pt/50pt,rectangle/fill/-50pt/-50pt,circle/fill/50pt/-50pt}{
    \begin{scope}[xshift=\xshift,yshift=\yshift]
    \tikzstyle{every node}=[\type,draw,\fill];
    \foreach \i in {0,20pt,40pt,60pt}{
      \foreach \j in {0,20pt,40pt,60pt}{
        \node (node\type\fill\i\j) at (\i,\j) {};
      }
    }
\end{scope}
  }
  %% \path
  %% (nodecircledraw20pt40pt) edge (nodecirclefill040pt)
  %% edge (noderectanglefill20pt20pt)
  %% edge (noderectangledraw60pt60pt)
  %% (nodecirclefill040pt) edge (noderectanglefill20pt20pt)
  %% edge (noderectangledraw60pt60pt)
  %% (noderectanglefill20pt20pt) edge (noderectangledraw60pt60pt)
  %% ;
  %% \path
  %% (nodecircledraw60pt60pt) edge (nodecirclefill40pt20pt)
  %% edge (noderectanglefill060pt)
  %% edge (noderectangledraw20pt40pt)
  %% (nodecirclefill40pt20pt) edge (noderectanglefill060pt)
  %% edge (noderectangledraw20pt40pt)
  %% (noderectanglefill060pt) edge (noderectangledraw20pt40pt)
  %% ;
  \path[thick]
  %%%%
  (nodecircledraw40pt60pt) edge (nodecirclefill20pt20pt)
  edge (noderectanglefill40pt60pt)
  edge (noderectanglefill20pt20pt)
  edge (noderectangledraw40pt20pt)
  edge (nodecirclefill60pt60pt)
  %edge (noderectanglefill40pt40pt)
  edge (noderectangledraw60pt60pt)
  %%%%%%%%%%%
  (nodecircledraw020pt) edge (nodecirclefill20pt20pt)
  edge (noderectanglefill40pt60pt)
  edge (noderectanglefill20pt20pt)
  edge (noderectangledraw40pt20pt)
  edge (nodecirclefill60pt60pt)
  %edge (noderectanglefill40pt40pt)
  edge (noderectangledraw60pt60pt)
  %%%%%%%%%%%%%%
  (nodecirclefill20pt20pt) edge (noderectanglefill40pt60pt)
  edge (noderectangledraw60pt60pt)
  edge (noderectanglefill20pt20pt)
  edge (noderectangledraw40pt20pt)
  %%%%%
  (nodecirclefill60pt60pt) edge (noderectanglefill40pt60pt)
  edge (noderectangledraw60pt60pt)
  edge (noderectanglefill20pt20pt)
  edge (noderectangledraw40pt20pt)
  %%%%%
  (noderectanglefill40pt60pt) edge (noderectangledraw60pt60pt)
  edge (noderectangledraw40pt20pt)
  %%%%%%%%%%%
  (noderectanglefill20pt20pt) edge (noderectangledraw60pt60pt)
  edge (noderectangledraw40pt20pt)
  ;
\end{tikzpicture}
\caption{Illustration of the storage process of a message $\mu$. In this setting the number of clusters is $c=4$, each containing $\ell=16$ units. The parameter $a$ is 2.}
\label{fig:storage}
\end{figure}

@@

		\begin{align*}
		&\tilde{\mu}'[(j-1)l+k] =\\ \bigg \{
  			&\begin{tabular}{cl}
  			$1$ & if $s[(j-1)\ell +k] \ge  \mbox{select}(\alpha, s[(j-1)\ell+1 \hdots j\ell])$ \\
  			$0$ & otherwise 
  		         \end{tabular}\;.
  		\end{align*}
                Thus we use an Heavyside function with a parameter depending on each cluster. $\tilde{\mu}'$ is the output of the algorithm after one iteration. The process can be repeated providing $\tilde{\mu}'$ as the new input to the network. Several stopping criterion can be used~\cite{Ala}. In the remaining of this work, we will consider the number of iterations to be fixed. Simulations show that increasing the number of iterations can result in significatively better performance.

@@

	\begin{align}
		\label{formula_density}
		d = 1 - \left( 1 - \left(\frac{a}{l}\right)^2 \right)^M 
	\end{align}		
	, recalling that $M$ is the number of messages in $\mathcal{M}$.

@@

	The network is a binary symmetric matrix with null diagonal and can therefore be stored in memory as $\frac{c(c-1) l^2}{2}$ bits. Since messages are not stored in an ordered fashion, the entropy of the set of messages is $\log_2(\frac{({l \choose a}^c)^M}{M!}) \mathop{=}_{M \rightarrow +\infty} M(c \log_2{l \choose a } - \log_2(M) + \frac{1}{\log 2} + o(1)) $ (thanks to  Stirling's formula). The ratio of information effectively stored in the network is $P_{retrieve} \times  \frac{2M \left(c \log_2{l \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)l^2}$.

	Ambiguities would occur in a perfect associative memory if at least two messages were identical over non-erased letters. The probability it doesn't happen is $ (1-{l \choose a}^{c - c_e})^{M-1}$.

	$\eta_M = P_{retrieve}  \frac{2 M\left(c \log_2{l \choose a } - \log_2(M) + \frac{1}{\log 2} \right)}{c(c-1)l^2} \times (1-(\frac{1}{{l \choose a}})^{c - c_e})^{-(M-1)}$
	%\frac{c}{(c-c_e) \log_2{l \choose a }}
